---
title: "HousePrices"
author: "Chetan"
date: "23/02/2022"
output: word_document
---

## Load Data

```{r load data}
# reading csv file
data <- read.csv('./Table2.1HousePrices-NoID.csv')
```
## Question 1:  
Write a function that takes SqFt and Brick (Yes or No) as inputs and returns the average price of all the houses which are less than or equal to the square feet and match the Brick type provided as arguments in the function. For example, if the function has 2000 and "No" as inputs, it should return the average of non-brick houses which are less than or equal to 2000 square feet in size.   

## Answer 1:  

```{r answer 1}
avg_fun <- function(sqft, brick){
        total<-0
        avg <- 0
        count<-0
        # iterating each rows
        for(i in 1:length(data$Price)){ 
                # applying condition if match then
                if(data$SqFt[i] <= sqft && data$Brick[i] == brick){ 
                        # price will added to total
                        total<- total + data$Price[i] 
                        # counting number of entries
                        count<- count + 1 
                }
        }
        # calculating average
        avg <- total / count 
        avg <- round(avg, 2)
        # now printing
        print(paste("Average price is: ",avg)) 
}

# calling function
avg_fun(2000,"No") 

```

## Question 2:
Write another function which also takes "Neighborhood" as an input in addition to SqFt and Brick as in (1). 

## Answer 2:

```{r answer 2}
avg_fun_hood <- function(sqft, brick, neighborhood){
        total<-0
        avg <- 0
        count<-0
        # iterating each rows
        for(i in 1:length(data$Price)){ 
                # applying condition if match then
                if(data$SqFt[i] <= sqft && data$Brick[i] == brick && data$Neighborhood == neighborhood){ 
                        # price will added to total
                        total<- total + data$Price[i] 
                        # counting number of entries
                        count<- count + 1 
                }
        }
        # calculating average
        avg <- total / count 
        avg <- round(avg, 2)
        # printing
        print(paste("Average price is: ",avg)) 
}

# calling function
avg_fun_hood(2200,"No", "East") 

```
Question 3:
Create a histogram of Price by changing the default values of several arguments of hist function. Your output should have proper title, axes labels and reasonable number of bins. 


## Answer 3:

```{r answer 3}
# ploting histogram
hist(data$Price, xlab="Price" , main="Histogram for Price", breaks = 5)

```


## Answer 4:


```{r answer 4}
avg_price_bedroom_using_for <- function(bedroom){
        total<-0
        avg <- 0
        count<-0
        # iterating each rows
        for(i in 1:length(data$Price)){ 
                # applying condition if match then
                if(data$Bedrooms[i] == bedroom){ 
                        # price will added to total
                        total<- total + data$Price[i] 
                        # counting number of entries
                        count<- count + 1 
                }
        }
        # calculating average
        avg <- total / count 
        # now printing
        print(paste("Average price is: ",avg)) 
}

# calling function
avg_price_bedroom_using_for(2) 



```

## Answer 5:


```{r answer 5}
avg_price_bedroom_using_while <- function(bedroom){
        total<-0
        avg <- 0
        count<-0
        # iterating each rows
        i <- length(data$Price)
        class(i)
        # Using while loop to check the condition 
        while(i >= 1){ 
                # using if to check number of bedrooms
                if(data$Bedrooms[i] == bedroom){ 
                        # price will added to total
                        total<- total + data$Price[i] 
                        # counting number of entries
                        count<- count + 1 
                }
                
                i = i - 1
                }
        # calculating average
        avg <- total / count 
        # printing result
        print(paste("Average price is: ",avg)) 
}

# calling function
avg_price_bedroom_using_while(2) 

```